
---
title: "Running an experiment with the SAA alongside other ability tests"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running an experiment with the SAA alongside other ability tests}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

[`psychTestR`](https://pmcharrison.github.io/psychTestR/articles/b-introduction) enables psychologists to chain together multiple psychology tests and questionnaires in one battery, allowing for data from several tests to be stored together in one place.

This vignette will show a quick example of how you can include several `psychTestR` tests together alongside the `SAA`.

First we install some tests. These tests were the ones used in Experiment 1 of our paper.

```{r eval = FALSE}

tests <- c(
    'pmcharrison/piat',
    'sebsilas/SAA',
    'pmcharrison/piat',
    'pmcharrison/mdt',
    'pmcharrison/mpt',
    'klausfrieler/JAJ',
    'fmhoeger/psyquest'
)

devtools::install_github(tests)

```

If they all installed correctly, we can proceed to put the tests together in a single timeline:

```{r eval = FALSE}


# Import the test libraries
library(psychTestR)
library(SAA)
library(PDT)
library(piat)
library(mdt)
library(mpt)
library(JAJ)
library(psyquest)

# For now, we need to do this:
library(psychTestRCAT) # call this after SAA for now

# A global password for all tests
password <- "demo"


timeline <- join(

  SAA(app_name = "my_research_project"),
  # The SAA num_items defaults are the same as used in the experiment: 6 long notes, 10 arrhythmic and 10 rhythmic melodies
  # By default, the SAA deploys the Goldsmiths Musical Sophistication Index Musical Training and Singing Abilities subscales

   # The code to do this manually (commented out) is:
  # GMS(admin_password = password, subscales = c("Musical Training", "Singing Abilities")),

  # Pitch Discrimination Task
  PDT(label = "PDCT", num_items = 15L),

  # Pitch Imagery Arrow Task
  piat(label = "PIAT", num_items = 15L),

  # Melodic Discrimination Test
  mdt(label = "MDT", num_items = 11L),

  # Mistuning Perception Test
  mpt(label = "MPT", num_items = 15L),

  # Jack and Jill Working Memory Test
  JAJ(label = "JAJ", num_items = 8L),

  # Make sure results are saved to disk
  elt_save_results_to_disk(complete = TRUE),

  # A "final_page" is required at the end of a psychTestR timeline
  final_page("You have completed the study!")
)


make_test(
  elts = timeline,
  opt = test_options(title = "Melody Singing Battery", admin_password = password))

```

