
---
title: "Creating custom pages to collect singing data."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating custom pages to collect singing data.}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

As mentioned in our paper, the `SAA` is built in a modular way, meaning functionality can be used from its dependent packages, like `musicassessr`.

`musicassessr` has a special page type called `record_audio_page`, which does just that: allows you to create a page which records and stores audio data. 

We're going to harness this and make our own function which returns a "Sing Happy Birthday" page. This is really just a `record_audio_page` with some custom text:

```{r message = FALSE, warning = FALSE}

library(musicassessr)

# Create a "Sing Happy Birthday Page"

sing_hbd <- function() {
  record_audio_page(label = "sing_hbd",
                    page_text = "Please sing happy birthday!",
                    get_answer = musicassessr::get_answer_simple_pyin_summary,
                    auto_next_page = TRUE)
}

```

Note that, for the `get_answer` function, we use a function which summarises what the user sung with some descriptive statistics. Type the following in your *R* console for more information:

```{r}

?musicassessr::get_answer_simple_pyin_summary

```


We can now include our new page, or a list of pages, if we wanted, by using the `append_trial_block_before` or `append_trial_block_after` arguments to the `SAA` functions.

1. Launch the `SAA` with the new Happy Birthday Page at the beginning of the protocol:


```{r eval = FALSE}

library(SAA)

SAA_standalone(app_name = "sing_hbd", 
               append_trial_block_before = sing_hbd())

```


2. Or the end of the protocol:



```{r eval = FALSE}

SAA_standalone(app_name = "sing_hbd",
               append_trial_block_after = sing_hbd())

```

3. Or even in your own custom timeline!


```{r eval = FALSE}

library(psychTestR)

password <- "demo"

timeline <- join(

  sing_hbd(),

  # Make sure results are saved to disk
  elt_save_results_to_disk(complete = TRUE),

  # A "final_page" is required at the end of a psychTestR timeline
  final_page("You have completed the study!")
)


make_test(
  elts = timeline,
  opt = test_options(title = "Melody Singing", admin_password = password))
  
```



By the way, a "Sing Happy Birthday" page is already packaged as part of `musicassessr`. Type the following into your *R* console for more information:

```{r}

?musicassessr::sing_happy_birthday_page

```


